Analysis: NAME

### 2019-12-28 abundance.Rmd
commit as of 12/28/2019

```{r}
root <- "data"
all_data <-
  tibble(
    sample = c("a", "b"),
    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

>>>>

```{r}
root <- "data/tsq_reports"
all_data <-
  tibble(
    sample = c("a", "b"),
    file = c("TSQ5934_mAx_TAC_2ml.xls", "TSQ5934_mAx_TAC_2ml.xls"),
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```
